\documentclass[a4paper,10pt]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{parskip}
\pagestyle{empty}

%--------------------
% Custom commands
\newcommand{\resumeItem}[1]{\item #1}
\newcommand{\resumeSubheading}[4]{
  \textbf{#1} \hfill #2 \\
  #3 \hfill #4 \\
}
\newcommand{\resumeSection}[1]{\vspace{6pt}\textbf{\large #1}\vspace{2pt}\hrule\vspace{4pt}}

\begin{document}

\begin{center}
  {\LARGE \textbf{Segni Mekonnen}} \\[2pt]
  Minnesota State University, Mankato \\[2pt]
  \href{mailto:segnimekonnen7@gmail.com}{segnimekonnen7@gmail.com} $\vert$ 
  \href{https://github.com/segnimekonnen7}{GitHub} $\vert$ 
  \href{https://www.linkedin.com/in/segni-mekonnen-16928125b}{LinkedIn}
\end{center}

\resumeSection{Education}
\resumeSubheading{B.S. in Computer Information Technology, Minor in Mathematics}{Expected 2026}{Minnesota State University, Mankato}{Dean's List}
\begin{itemize}[leftmargin=*, noitemsep]
  \resumeItem{Relevant Coursework: Machine Learning, Data Structures, Algorithms, Calculus, Linear Algebra, Probability, Statistics}
\end{itemize}
\textbf{Certifications:} Andrew Ng's Machine Learning Specialization (Coursera, In Progress), Harvard Machine Learning (edX)

\resumeSection{Technical Skills}
Python, SQL, Git, Docker, Jupyter, Flask, Streamlit, TensorFlow, PyTorch, scikit-learn, pandas, NumPy, spaCy, OpenAI API

\resumeSection{Projects}
\textbf{AI Internship Finder Bot} \\[-2pt]
\begin{itemize}[leftmargin=*, noitemsep]
  \resumeItem{Scrapes job platforms, uses NLP to match internships to resumes, and sends real-time alerts.}
  \resumeItem{Matched 100+ internship listings to user profiles in initial tests.}
  \resumeItem{Achieved approximately 80\% accuracy in resume-job matching (manual review).}
  \resumeItem{Processed and analyzed several thousand job postings from multiple platforms.}
  \resumeItem{\textit{Tech: Python, BeautifulSoup, spaCy, Flask, OpenAI API, GitHub}}
\end{itemize}

\textbf{AI Interview Prep Assistant} \\[-2pt]
\begin{itemize}[leftmargin=*, noitemsep]
  \resumeItem{Mock interview platform that generates questions using OpenAI’s GPT API and provides real-time feedback.}
  \resumeItem{Generated hundreds of unique interview questions for users.}
  \resumeItem{Used by 10+ students for interview practice in the first month.}
  \resumeItem{Received positive feedback from users.}
  \resumeItem{\textit{Tech: Python, OpenAI API, Streamlit, GitHub}}
\end{itemize}

\textbf{Open Source Contributor – Omdena} \\[-2pt]
\begin{itemize}[leftmargin=*, noitemsep]
  \resumeItem{Contributed to a global AI-for-good project focused on NLP for education access.}
  \resumeItem{Improved text preprocessing pipeline, increasing model F1 score by 12\%.}
  \resumeItem{Collaborated with 15+ data scientists and engineers.}
\end{itemize}

\resumeSection{Leadership \& Extracurriculars}
\textbf{Boy Scout Leader | Boy Scouts of Ethiopia} \hfill 2015--2018
\begin{itemize}[leftmargin=*, noitemsep]
  \resumeItem{Selected to represent Ethiopia at the 2017 World Scout Jamboree, collaborating with scouts from 100+ countries.}
  \resumeItem{Led and mentored teams during national events and community service projects.}
  \resumeItem{Organized team-building exercises and managed diverse groups in dynamic environments.}
\end{itemize}

\resumeSection{Soft Skills}
Teamwork, Communication, Leadership, Problem-solving, Adaptability

\end{document} 